A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
as agreed, TODO for JP ;-)
fill a bit CM

\subsection{Kinematics}

Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$
is defined via the mapping $\gz x = \gz \varphi (\gz X,t)$.

Linear deformation map is assumed for the macroscopic point
\begin{align}
\d \gz x = \gz F \cdot \d \gz X,
\end{align}
where $\gz F := \gz \nabla_{X} \, \gz \varphi$ is the deformation gradient.

\subsection{Kinetics}

For conservative systems the total potential energy is introduced as
\begin{align}
\mcl E = \int_{\mcl B_0} \mcl U_0(\gz \varphi, \gz F; \gz X) \,
\end{align}
that must be stationary in order for the system to be in equilibrium:
\begin{align}
\delta \mcl E = 0 \, .
\label{eq:stationary}
\end{align}

>>>>

{\color{red}
TODO: JP please fill in this part based on your other papers.
}

Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$
is defined via the mapping $\gz x = \gz \varphi (\gz X,t)$.
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \gz \nabla_{X} \, \gz \varphi$ is the deformation gradient.
For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz \varphi, \gz F; \gz X) \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, and $\mcl \psi$ denotes the strain-energy per unit reference volume.

The principal of stationary potential energy requires that the directional derivative with respect to the displacement $\gz u$
\begin{align}
\delta \mcl E = \frac{\d}{\d \epsilon} \mcl E (\gz u + \epsilon \delta \gz u) \Bigr\rvert_{\epsilon=0}  = 0 \, .
\label{eq:stationary}
\end{align}
vanishes for all directions $\delta \gz u$ at the equilibrium state.
The vector field $\delta \gz u$ should be equal to zero at the Dirichlet boundary $\partial \mcl B_0^D := \partial \mcl B_0 \setminus \partial \mcl B_0^N$.
